### 2015-11-20 section/3_redundancy.tex
shrink back to 11 pages

The implementation of checking cross-iteration redundancy is straightforward.
\comment{
We will record a sequence of $<InstID, Value>$ pair for every monitored
iteration, with each $InstID$ representing a unique source instruction.
We consider two iterations to be redundant, if their sequences are exactly the
same. To make sure a loop contains sufficient redundant computation, 
}
We calculate a loop's \textit{cross-iteration redundancy rate} --- dividing 
the total number of iterations in the loop by the number of distinct iterations.
The smaller the rate is, with 1 being the minimum possible value, 
the less cross-iteration redundancy the loop contains.

The implementation of checking cross-loop redundancy goes through several
steps. First, for $k$ dynamic instances of a static loop $L$ that appear
at run time, denoted as $l_1$, $l_2$,
..., $l_k$, we check whether redundancy exists between $l_1$ and $l_2$, 
$l_2$ and $l_3$, and so on. Second, we compute a 
\textit{cross-loop redundancy rate} for $L$
--- dividing the number of redundant pairs by $k-1$.
The smaller the rate is, with 0 being the minimum possible value, the
less cross-loop redundancy $L$ contains.
Here we only check redundancy between consecutive loop instances, because  
checking the redundancy between every pairs of loop
instances is time consuming.

>>>>

The implementation of checking cross-iteration redundancy is straightforward.
\comment{
We will record a sequence of $<InstID, Value>$ pair for every monitored
iteration, with each $InstID$ representing a unique source instruction.
We consider two iterations to be redundant, if their sequences are exactly the
same. To make sure a loop contains sufficient redundant computation, 
}
We calculate a loop's \textit{cross-iteration redundancy rate} based on
the number of (distinct) iterations in a loop:
Rate$_\text{C.I.}$ = $1 - \frac{\text{\# of distinct iterations}}{\text{\# of iterations}}$.
This rate ranges between 0 and 1, the smaller it is
the less redundancy the loop contains.

Checking cross-loop redundancy goes through several
steps. First, for $k$ dynamic instances of a static loop $L$ that appear
at run time, denoted as $l_1$, $l_2$,
..., $l_k$, we check whether redundancy exists between $l_1$ and $l_2$, 
$l_2$ and $l_3$, and so on. Second, we compute a 
\textit{cross-loop redundancy rate} for $L$:
Rate$_\text{C.L.}$ = $\frac{\text{\# of redundant pairs}}{\text{\# of pairs}}$
(In this example, $\text{\# of pairs}$ is $k-1$).
This rate ranges between 0 and 1, the smaller it is the less redundancy
$L$ contains.
We only check redundancy between consecutive loop instances, because  
checking that between every pairs of loop
instances is time consuming.

### 2015-11-20 section/5_exper.tex
shrink back to 11 pages

\begin{table}
  \centering
  \small
  \newcommand{\Yes}[0]{\checkmark}
  \newcommand{\No}[0]{-}
  \begin{tabular}{lcccccc}
    \toprule
   {\bf BugID}           &  {\bf 0*1?}          &  {\bf [0$|$1]*}             &{\bf C-I$_b$}            &{\bf C-I$_m$}          &   {\bf C-L}     & {\bf Total}  \\
   \midrule
   Mozilla347306         &   -                  & -                           & -                       & -                     &   -             & -\\
   Mozilla416628         &   -                  & -                           & -                       & -                     &   -             & -\\
   Mozilla490742        &   -                  & -                           & -                       & -                     &   -             & -\\
   Mozilla35294         &   -                  & -                           & -                       & -                     &   -             & -\\ 
   Mozilla477564         &   -                  & -                           & -                       & -                     &   -             & -\\
   \midrule 
   MySQL27287            &   -                  & 0$_1$                       & -                       & -                     &   -             & 0$_1$\\
   MySQL15811            &   -                  & -                           & -                       & -                     &   -             & -\\ 
   \midrule    
   Apache32546           &   -                  & -                           & -                       & -                     &   -             & -\\
   Apache37184           &   -                  & -                           & -                       & -                     &   -             & -\\
   Apache29742       &   -                  & -                           & -                       & -                     &   -             & -\\ 
   Apache34464           &   -                  & -                           & -                       & -                     &   -             & -\\
   Apache47223           &   -                  & -                           & -                       & -                     &   -             & -\\
   \midrule
   GCC46401              &   -                  & 0$_1$                       & -                       & -                     &   -             & 0$_1$\\
   GCC1687               &   -                  & -                           & -                       & -                     &   -             & -\\
   GCC27733            &   -                  & -                           & -                       & -                     &   -             & - \\
   GCC8805               &   -                  & 0$_1$                       & -                       & -                     &   -             & 0$_1$\\
   GCC21430              &   0$_1$              & 0$_3$                       & -                       & 0$_1$                 &   0$_1$         & 0$_6$\\
   GCC12322              &   0$_1$              & 0$_1$                       & -                       & 0$_1$                 &   0$_1$         & 0$_4$\\
\bottomrule
   \end{tabular}
  %\nocaptionrule
  \caption{False positives of \Tool for top 5 loops reported by 
    statistical debugging for each benchmark. `-': no false positive. $x_y$: real ($x$) and benign false positives ($y$).
}
  \label{tab:top5}
\end{table}

@@

The accuracy of \Tool benefits from its run-time analysis.
For example, there are seven benchmarks in total that each contains
one loop, which generates side effect only
in its last iteration. Without run-time information, \Tool would judge
all of them as inefficient (i.e., 0*1? resultless). Fortunately,
\Tool run-time analysis counts the total number of loop iterations and
correctly identifies three of them as truly inefficient and severe enough
to cause the corresponding performance problem.

@@

The benefit of static optimization is also non-trivial. 
For example, for MySQL\#15811 and MySQL\#27287, static analysis alone can
judge that they do not contain cross-iteration redundancy: the computation of 
each iteration depends on loop induction variables, which are natually different
in different iterations. Consequently, run-time overhead is completely
eliminated for these two benchmarks.
As another example, the buggy loops of MySQL\#27287 and MySQL\#15811 access 
arrays. 
After changing to tracking the initial and ending memory-access addresses
of the array, instead of the content of the whole array accesses,
the overhead is reduced from 11.77\% to 1.66\% for MySQL\#27287, 
and from 20.46\% to 0.03\% for MySQL\#15811 respectively 
(sampling is conducted consistently here).

@@

\paragraph{Resultful and redundancy rate}
Since the severity of resultless and redundant loops depends on
workload, it is natural that \Tool uses two thresholds in its diagnosis.
In fact, the diagnosis results are largely insensitive to the threshold
setting. For example, the results would remain the same when
changing the redundancy rate threshold from 0.5 to any value between about
0.1 and 0.66. We will have 1 more false negative and 1 fewer benign report, 
when the rate is 0.75. The trend is similar for resultless
loop checking.

Our default setting %is obtained based on our experience
should work for many problems.
Developers can adjust these thresholds. 
They can even get rid of threshods, and only
use the raw values of resultful/redundancy rates to understand
the absolute and relative (in)efficiency nature of suspicious 
loops. Based on our experiments, the difference between efficient and inefficient
loops is usually obvious, based on these rates.

>>>>

\begin{table}
  \centering
  \small
  \newcommand{\Yes}[0]{\checkmark}
  \newcommand{\No}[0]{-}
  \begin{tabular}{lcccccc}
    \toprule
   {\bf BugID}           &  {\bf 0*1?}          &  {\bf [0$|$1]*}             &{\bf C-I$_b$}            &{\bf C-I$_m$}          &   {\bf C-L}     & {\bf Total}  \\
   \midrule
   Mozilla347306         &   -                  & -                           & -                       & -                     &   -             & -\\
   Mozilla416628         &   -                  & -                           & -                       & -                     &   -             & -\\
   Mozilla490742        &   -                  & -                           & -                       & -                     &   -             & -\\
   Mozilla35294         &   -                  & -                           & -                       & -                     &   -             & -\\ 
   Mozilla477564         &   -                  & -                           & -                       & -                     &   -             & -\\
   \midrule 
   MySQL27287            &   -                  & 0$_1$                       & -                       & -                     &   -             & 0$_1$\\
   MySQL15811            &   -                  & -                           & -                       & -                     &   -             & -\\ 
   \midrule    
   Apache32546           &   -                  & -                           & -                       & -                     &   -             & -\\
   Apache37184           &   -                  & -                           & -                       & -                     &   -             & -\\
   Apache29742       &   -                  & -                           & -                       & -                     &   -             & -\\ 
   Apache34464           &   -                  & -                           & -                       & -                     &   -             & -\\
   Apache47223           &   -                  & -                           & -                       & -                     &   -             & -\\
   \midrule
   GCC46401              &   -                  & 0$_1$                       & -                       & -                     &   -             & 0$_1$\\
   GCC1687               &   -                  & -                           & -                       & -                     &   -             & -\\
   GCC27733            &   -                  & -                           & -                       & -                     &   -             & - \\
   GCC8805               &   -                  & 0$_1$                       & -                       & -                     &   -             & 0$_1$\\
   GCC21430              &   0$_1$              & 0$_3$                       & -                       & 0$_1$                 &   0$_1$         & 0$_6$\\
   GCC12322              &   0$_1$              & 0$_1$                       & -                       & 0$_1$                 &   0$_1$         & 0$_4$\\
\bottomrule
   \end{tabular}
  %\nocaptionrule
\vspace{-0.1in}
  \caption{False positives of \Tool for top 5 loops reported by 
    statistical debugging for each benchmark. `-': no false positive. $x_y$: real ($x$) and benign false positives ($y$).
}
  \label{tab:top5}
\end{table}

@@

The accuracy of \Tool benefits from its run-time analysis.
For example, there are 7 benchmarks in total that each contains
a loop that generates side effect only
in its last iteration. Without run-time information, \Tool would judge
all of them as inefficient (0*1? resultless). Fortunately,
\Tool run-time counts the total number of iterations and
correctly identifies 3 of them as truly inefficient and severe enough
to cause the corresponding performance problem.

@@

The benefit of static optimization is also non-trivial. 
For example, for MySQL\#15811 and MySQL\#27287, static analysis alone can
judge that they do not contain cross-iteration redundancy: the computation of 
each iteration depends on loop induction variables, which are naturally different
in different iterations. Consequently, run-time overhead is completely
eliminated for these two benchmarks.
As another example, the buggy loops of MySQL\#27287 and MySQL\#15811 access 
arrays. 
After changing to tracking the initial and ending memory-access addresses
of the array, instead of the content of the whole array accesses,
the overhead is reduced from 11.77\% to 1.66\% for MySQL\#27287, 
and from 20.46\% to 0.03\% for MySQL\#15811 respectively 
(sampling is conducted consistently here).

@@

\paragraph{Resultful and redundancy rate}
Since the severity of resultless and redundant loops depends on
workload, it is natural that \Tool uses two thresholds in its diagnosis.
In fact, the diagnosis results are largely insensitive to the threshold
setting. For example, the results would remain the same when
changing the redundancy rate threshold from 0.5 to any value between about
0.1 and 0.7. We will have 1 more false negative and 1 fewer benign false positive, 
when the rate is 0.75. The trend is similar for resultless
loop checking.

Our default setting %is obtained based on our experience
should work for many problems.
Developers can adjust these thresholds. 
They can even get rid of thresholds, and only
use the raw values of resultful/redundancy rates to understand
the absolute and relative (in)efficiency nature of suspicious 
loops. Based on our experiments, the difference between efficient and inefficient
loops is usually obvious, based on these rates.
